A Machine Learning Approach to MLB Catcher Framing

### 2021-12-09 Slides.Rmd
Add boosting

- 3 Fold Cross Validation on Random Forest  
  - Tested on nodesizes of 10, 30, 50, 70, 90 | 500 trees
  - Compared Out-Of-Bag Error 
```{r}
load("Data/pitchData.Rda")
load("Model-Outputs/random-forest.Rda")

@@

>>>>

- 3 Fold Cross Validation on Random Forest  
  - Tested on nodesizes of 10, 30, 50, 70, 90 | 500 trees
  - Compared Out-Of-Bag Error 
```{r, echo=FALSE}
load("Data/pitchData.Rda")
load("Model-Outputs/random-forest.Rda")

@@

## Boosting

```{r, echo=FALSE}
load("Model-Outputs/boosting.Rda")

ggplot(df_gbm_final, aes(x = interaction_depth, y = accuracy, color = as.character(lambda))) +
  geom_line() +
  theme_minimal()+
  geom_point() +
  geom_point(aes(x = 16, y = 0.935), color = "red") +
  labs(x = "Accuracy", y = "Interactin Depth",
       color = "Shrinkage",
       y = "Boosting Accuracy by Interaction Depth and Shrinkage")
```
